Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-11-23 Text/2024PresentationsChina.tex
Update 2024PresentationsChina.tex

>>>>

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{The test based on the Shannon entropy}
\centering
\includegraphics[width=0.7\linewidth]{R1-Identifying-Heterogeneity-in-SAR-Data-with-New-Test-Statistics_files/figure-latex/Plot_density-1}
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data}
\centering
\includegraphics[width=.42\linewidth]{../Figures/PNG/Phantom1}
\includegraphics[width=.57\linewidth]{../Figures/PNG/Phantom_label/Phantom_labels}
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to simulated data: $S_{\widehat{\text{CV}}}$, $S_{\widehat{\text{CV}_{\text{MnAD}}}}$, and $S_{\widetilde{H}_{\text{AO}}}$ $p$-values}
\centering
{\includegraphics[width=.32\linewidth]{../Figures/PNG/cv_pvalues_Phantom_4_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/mnad_p_values_Phantom_mnad_7_z1} }
{\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_Phantom_4_z1_200b} }
\end{frame}
}

{\setbeamercolor{background canvas}{bg=anti-flashwhite}
\begin{frame}{Application to Sentinel~2 data}
\centering
\includegraphics[width=.335\linewidth]{../Figures/PNG/Sentinel2_Illinois_lake}
\includegraphics[width=.32\linewidth]{../Figures/PNG/lake_512}
\includegraphics[width=.32\linewidth]{../Figures/PNG/H_pvalue_lake_512_36L_AO_100b}
\end{frame}
}
